15th International Satisfiability Modulo Theories Competition (SMT-COMP 2021): Rules and Procedures

### 2021-05-04 rules/rules21.tex
some more trivial updates for this year

\author{%
Haniel Barbosa\\
Universidade Federal de Minas Gerais\\
Brazil\\
{\small\href{mailto:hbarbosa@dcc.ufmg.br}{\texttt{hbarbosa@dcc.ufmg.br}}}\\
\and
Jochen Hoenicke\\
Universit\"at Freiburg\\
Germany\\
{\small\href{mailto:hoenicke@informatik.uni-freiburg.de}{\texttt{hoenicke@informatik.uni-freiburg.de}}}\\
\and
Antti Hyvarinen (chair)\\
Universita della Svizzera italiana \\
Switzerland \\
{\small\href{mailto:antti.hyvaerinen@usi.ch}{\texttt{antti.hyvaerinen@usi.ch}}} \\
}

@@

\header{Benchmark selection.} \label{benchmark-selection}
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks
% \textbf{except} the \challtrack,
the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy / uninteresting benchmarks.}
  For the following tracks, all benchmarks that can be
  considered as easy or uninteresting based on the following criteria
  will be removed.
  \begin{itemize}
    \item \emph{\maintrack.} All benchmarks that were solved by all
      solvers (including non-competitive solvers) in less than one second in
          the corresponding track in 2018 or 2019.
    \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
  \end{itemize}
\item \emph{Cap the number of instances in a division.}
  The number of benchmarks in a division based on the size of the
  corresponding logic in SMT-LIB will be limited as follows.
  Let $n$ be the number of benchmarks in an SMT-LIB logic, then
  \begin{enumerate}
  \vspace{-1ex}
    \item \label{bench-sel-300} if $n \le 300$, all instances will be selected;
  \item \label{bench-sel-600} if $300 < n \leq 750$, a subset of 300 instances
    from the logic will be selected;
  \item \label{bench-sel-more} and if $n > 750$,
      40\% of the benchmarks of the logic will be selected.
  \end{enumerate}
\end{enumerate}
%
The selection process in cases \ref{bench-sel-600} and \ref{bench-sel-more}
above will guarantee the inclusion of new benchmarks by first picking randomly
one benchmark from each new benchmark family.  The rest of the benchmarks will
be chosen randomly from the remaining benchmarks using a uniform distribution.
%
The benchmark selection script will be publicly available at
\url{https://github.com/SMT-COMP/smt-comp/tree/master/tools} and
will use the same random seed as the rest of the competition.  The set of
benchmarks selected for the competition will be published when the competition
begins.

>>>>

\author{%
Haniel Barbosa\\
Universidade Federal de Minas Gerais\\
Brazil\\
{\small\href{mailto:hbarbosa@dcc.ufmg.br}{\texttt{hbarbosa@dcc.ufmg.br}}}\\
\and
Jochen Hoenicke (chair)\\
Universit\"at Freiburg\\
Germany\\
{\small\href{mailto:hoenicke@informatik.uni-freiburg.de}{\texttt{hoenicke@informatik.uni-freiburg.de}}}\\
\and
Antti Hyvarinen\\
Universita della Svizzera italiana \\
Switzerland \\
{\small\href{mailto:antti.hyvaerinen@usi.ch}{\texttt{antti.hyvaerinen@usi.ch}}} \\
}

@@

\header{Benchmark selection.} \label{benchmark-selection}
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks
% \textbf{except} the \challtrack,
the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy / uninteresting benchmarks.}
  For the following tracks, all benchmarks that can be
  considered as easy or uninteresting based on the following criteria
  will be removed.
  \begin{itemize}
    \item \emph{\maintrack.} All benchmarks that were solved by all
      solvers (including non-competitive solvers) in less than one second in
          the corresponding track in 2018, 2019, and 2020.
    \item \emph{\ucoretrack.} All benchmarks with only a single assertion.
  \end{itemize}
\item \emph{Cap the number of instances in a division.}
  The number of benchmarks in a division based on the size of the
  corresponding logic in SMT-LIB will be limited as follows.
  Let $n$ be the number of benchmarks in an SMT-LIB logic, then
  \begin{enumerate}
  \vspace{-1ex}
    \item \label{bench-sel-300} if $n \le 300$, all instances will be selected;
  \item \label{bench-sel-600} if $300 < n \leq 750$, a subset of 300 instances
    from the logic will be selected;
  \item \label{bench-sel-more} and if $n > 750$,
      40\% of the benchmarks of the logic will be selected.
  \end{enumerate}
\end{enumerate}
%
The selection process in cases \ref{bench-sel-600} and \ref{bench-sel-more}
above will guarantee the inclusion of new benchmarks by first picking randomly
one benchmark from each new benchmark family.  The rest of the benchmarks will
be chosen randomly from the remaining benchmarks using a uniform distribution.
%
The benchmark selection script will be publicly available at
\url{https://github.com/SMT-COMP/smt-comp/tree/master/tools} and
will use the same random seed as the rest of the competition.  The set of
benchmarks selected for the competition will be published when the competition
begins.
